\chapter{Summary}
Since early 2017, we have been working on designing and setting up Cryptomanuals, a research and consultancy company which focuses mainly on the transformation within the financial ecosystem.  We present broader research into the state of the global economy and the emergence of new technology, especially blockchain, Bitcoin and cryptocurrencies.\medskip

We have personally experienced the massive hype which resulted in the speculative cryptocurrency bull run and boom of late 2017. We have also weathered the long and dramatic 'crypto winter' which has been moving sideways throughout 2018. All this time, we have feverishly been researching ever more information to enhance our understanding of this environment.\medskip 

From day one, we have been intrigued with the original idea behind Bitcoin and blockchain technology. During our research, we have both experienced and realized that there is an enormous 'knowledge gap' when it comes to people's understanding about monetary history, monetary policy and about the fundamentals of money in the first place.\medskip

We believe that this transition heralds the beginning of a new economic era, of an inclusive economy, where people's (intellectual) contributions are valued and rewarded according to the added value they bring to the economy as a whole, their immediate environment, community or family and friends. In our main report, we inform people of what is going on in the global economy, provide some historical context and point out one of the most significant opportunities and wealth transfers of our lifetimes. Even though we stress radical change appears to be imminent, most people still refuse to see what is right in front of them. 

\begin{quotation}

  \textit{\say{In the midst of every crisis, lies great opportunity.}}
  \begin{flushright}
    \small{--- \textbf{Einstein, Albert}}
  \end{flushright}

\end{quotation}

The cryptomanual provides you with all the information you need to start investing in - and learning about - blockchain and cryptocurrencies. It is extensive and offers much-needed insights relating to pressing social and economic macro developments driving these disruptive and emerging markets.\medskip 

Even though we are very positive regarding what the future has in store, we cannot help but share the sentiment that the financial system will undoubtedly go into a global recession if it does not change radically. If it doesn't, billions of people around the world are going to be affected. The world has to shake off the illusion that a debt-based fiat currency model is somehow good for our economy and snap back to reality, as we have done multiple times throughout history. Ultimately, it is about informing, warning and preparing people to take action today, to safeguard their financial future of tomorrow.