\clearpage

\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{25}


% BOOKS, PAPERS & ARTICLES %
\section*{Books, Papers \& Articles}

\bibitem{Inglehart}
Inglehart, R., and Norris, P. 2016. \emph{Trump, Brexit, and the rise of populism: Economic have-nots and cultural backlash.} HKS Working Paper No. RWP16-026.

\bibitem{Rodrik}
Rodrik, D. 2018. \emph{Populism and the economics of globalization.} Journal of International Business Policy, 1(1-2), 12-33.

\bibitem{Timmer}
Timmer, M. P., Erumban, A. A., Los, B., Stehrer, R., de Vries, G. J. 2014. \emph{Slicing up global value chains.} Journal of Economic Perspectives, 28(2), 99-118.

\bibitem{Winters}
Winters, L. A. 2002. \emph{Trade liberalisation and poverty: what are the links?} World Economy, 25(9), 1339-1367.

\bibitem{Brynjolfsson}
Brynjolfsson, E., McAfee, A. 2014. \emph{The second machine age: Work, progress, and prosperity in a time of brilliant technologies. (First ed.)} New York, NY: W.W. Norton \& Company.

\bibitem{Pikkety}
Piketty, T. 2014. \emph{Capital in the twenty-first century.} Cambridge Massachusetts: Belknap Press of Harvard University Press.

\bibitem{Autor}
Autor, D. 2015. \emph{Why Are There Still So Many Jobs? The History and Future of Workplace Automation.} Journal of Economic Perspectives, 29(3), pp. 3-30.

\bibitem{Nassim}
 Taleb, N. N. 2015. \emph{The Black Swan: The Impact of the Highly Improbable.} Random House.

\bibitem{debunkingeconomics}
Keen, S. 2011. \emph{Debunking economics: The naked emperor dethroned?}
London. Zed Books Ltd.

\bibitem{4th_Revolution}
Schwab, K. 2016. \emph{The Fourth Industrial Revolution: what it means and how to respond.} [10-02-2019].\\ \url{https://www.weforum.org/agenda/2016/01/the-fourth-industrial-revolution-what-it-means-and-how-to-respond/}

\bibitem{Global_Transformations}
World Economic Forum. \emph{Mapping Global Transformations.} [10-02-2019].\\ \url{https://toplink.weforum.org/knowledge/explore}

\bibitem{sapiens}
 Harari, Y. N. 2014. \emph{Sapiens: A Brief History of Humankind.} 
 Harper, New York City, U.S.

\bibitem{homodeus}
 Harari, Y. N. 2016. \emph{Homo Deus: A Brief History of Tomorrow.}
 Harvill Secker, London, U.K.

\bibitem{21lessons21th century}
 Harari, Y. N. 2018. \emph{21 Lessons for the 21$^{st}$ Century.}
 Spiegel \& Grau, Jonathan Cape, New York City, U.S., London, U.K.

\bibitem{goldsilver}
 Maloney, M. 2012. \emph{Guide To Investing in Gold \& Silver: Protect Your Financial Future.}
 WealthCycle Press.

\bibitem{blockchainrevolution}
 Tapscott, A., and Tapscott, D. 2012. \emph{Blockchain Revolution: How the Technology Behind Bitcoin Is Changing Money, Business, and the World.} Penguin Random House, New York City, U.S.

\bibitem{bitcoinstandard}
 Saifedean, A. 2018. \emph{The Bitcoin Standard: The Decentralized Alternative to Central Banking.}
 Wiley \& Sons, Inc., Hoboken, New Jersey.

\bibitem{threatmodelling}
Burton, K., and Li, A. 2018. \emph{A First Look at Digital Security.}\\ \url{https://www.accessnow.org/first-look-digital-security/}

\bibitem{financialinclusion}
World Bank Group. \emph{The Global Findex Database 2017. Measuring Financial Inclusion and the Fintech Revolution.} [26-10-2018].\\ \url{https://openknowledge.worldbank.org/bitstream/handle/10986/29510/9781464812590.pdf}

\bibitem{inequality.org}
Inequality. \emph{The Facts that Define Our Grand Divides.} 2018. [28-02-2019].\\ \url{https://inequality.org/facts/}

\bibitem{financializationeconomy}
Epstein, G.A. 2005. \emph{Financialization and the world economy.}  Edward Elgar Publishing. 

\bibitem{killingthehost}
Hudson, M. 2015. \emph{Killing the Host: How Financial Parasites and Debt Bondage Destroy the Global Economy.} CounterPunch.

\bibitem{makesensefinancialization}
Zwan, N. 2014. \emph{Making sense of financialization.} Socio-Economic Review 12: 99129. 

\bibitem{creditcardblues}
Hodson, R., Dwyer R.E., and Neilson, L.A. 2014. \emph{Credit Card Blues: The Middle Class and the Hidden Costs of Easy Credit.} The Sociological Quarterly 55: 315-40. 

\bibitem{financializationofcapitalism}
Foster, J.B. 2007. \emph{The financialization of capitalism.} Monthly Review Research Library, 58: 1-14. 

\bibitem{chinasocialscores}
Ma, A. 2018. \textit{China has started ranking citizens with a creepy 'social credit' system.} 
Business Insider. [05-11-2018]: Amsterdam.\\
\url{https://www.businessinsider.nl/china-social-credit-system-punishments-and-rewards-explained-2018-4/?international=true&r=US}

\bibitem{Baldwin} Baldwin, R. E., Evenett, S. J. 2015. \emph{Value creation and trade in 21st century manufacturing.} Journal of Regional Science, 55(1), 31-50.

\bibitem{Herradi} El Herradi, M., Leroy, A. 2019. \emph{Monetary policy and the top one percent: Evidence from a century of modern economic history.} De Nederlandsche Bank Working Paper No. 632.

\bibitem{FRED}
St. Louis FED. Economic Data. \emph{Federal Reserve Bank of St. Louis - Economic Research.}\\
\url{https://fred.stlouisfed.org/}

\bibitem{weimarhyperinflation}
Businessinsider. \emph{Weimar: the truth about history's most infamous hyperinflation horror story.}
2013. [24-06-2019].\\
\url{https://www.businessinsider.com/weimar-germany-hyperinflation-explained-2013-9}

\bibitem{fiattozero1}
Evolvingwealth. \emph{Why the value of FIAT money will always go to zero.} 2015. [26-06-2019].\\
\url{https://www.evolvingwealth.org/value-fiat-money-goes-to-zero/}

\bibitem{fiattozero2}
Truth is treason. \emph{A look at the past: all fiat currencies collapse and fail.}
2011. [24-06-2019].\\
\url{http://www.truthistreason.net/a-look-at-the-past-all-fiat-currencies-collapse-and-fail}

\bibitem{lastamericanvagabond}
The Last American Vagabond.
\emph{Bitcoin: A complete overview - a world monetary revolution or a speculative bubble about to burst?} 2016.\\
\url{http://www.thelastamericanvagabond.com/top-news/complete-overview-bitcoin/}

\bibitem{PwCBlockchain}
PwC. \emph{Blockchain is here. What's your next move?} 2018.\\
\url{https://www.pwc.com/gx/en/issues/blockchain/blockchain-in-business.html}

\bibitem{IOT}
Harbor Research, Postscapes. \emph{What Is The \say{Internet of Things}?} 2018.\\
\url{https://www.postscapes.com/what-exactly-is-the-internet-of-things-infographic/}

\bibitem{economist}
Economist. \emph{The worlds most valuable resource. Measuring Financial Inclusion and the Fintech Revolution.} [10-10-2017].\\
\url{https://www.economist.com/leaders/2017/05/06/the-worlds-most-valuable-resource-is-no-longer-oil-but-data}

\bibitem{mauldineconomics}
Mauldin Economics. \emph{Everything bubble.} [01-12-2017].\\ \url{https://www.mauldineconomics.com/EDITORIAL/infographic-the-everything-bubble-is-ready-to-pop}

\bibitem{businessinsider}
Business Insider. \emph{Market capitalization S\&P 500.} [20-06-2019].\\
\url{https://markets.businessinsider.com/index/market-capitalisation/s&p_500}

\bibitem{Ethos3}
Ethos. \emph{What are cryptocurrency wallets, private keys and addresses.} [20-05-2019].\\
\url{https://www.ethos.io/what-are-cryptocurrency-wallet-private-keys-addresses}

\bibitem{finra}
Finra. \emph{Key investing concepts} [20-05-2019].\\
\url{https://www.finra.org/investors/key-investing-concepts}

\bibitem{investopedia_economiccycles}
Investopedia. \emph{What is the Economic Cycle} [15-11-2018].\\
\url{https://www.investopedia.com/terms/e/economic-cycle.asp}

\bibitem{howmuch}
How much. \emph{Cryptocurrency market of 2018 in perspective.} [10-02-2018].\\
\url{https://howmuch.net/articles/worlds-money-in-perspective-2018}

\bibitem{businesscycle}
Your article library. \emph{Business cycle excluding and including a generic growth trend} [15-03-2019].\\
\url{http://www.yourarticlelibrary.com/macro-economics/theories-macro-economics/business-cycles-meaning-phases-features-and-theories-of-business-cycle/38063}

\bibitem{bearandbull}
Brightscope. \emph{ Market psychology drives bear and bull markets} [15-03-2019].\\
\url{https://www.brightscope.com/financial-planning/advice/article/30367/Breaking-The-Emotional-Cycle-Of-Investing}

\bibitem{EllenBrown} The Web of Debt Blog. \emph{You Can't Taper a Ponzi Scheme: Time to Reboot.} [02-10-2017].\\ \url{https://ellenbrown.com/2014/07/25/you-cant-taper-a-ponzi-scheme-time-to-reboot}

%% REPORTS %%

\section*{Reports}

\bibitem{bitcoinwhitepaper}
Nakamoto, S. 2008. \emph{Bitcoin: A Peer-to-Peer Electronic Cash System.}\\
\url{https://bitcoin.org/bitcoin.pdf}

\bibitem{Ethos1}
Ethos.
\emph{Balancing Decentralization: Value and Utility of Tokens Within Inclusive Financial Ecosystems} 2017/2018. [28-02-2019].\\
\url{https://www.ethos.io/blockchain-finance/}

\bibitem{Ethos2}
Ethos.
\emph{Ethos Token Classification System: A Framework for Understanding Types of Blockchain Based Tokens} 2017/2018. [28-02-2019].\\
\url{https://www.ethos.io/blockchain-finance/}

\bibitem{worldinequalityreport}
The World Inequality Lab.
\emph{World Inequality Report.} 2018. [28-02-2019].\\
\url{https://wir2018.wid.world/}

\bibitem{OECDinequalities}
OECD. \emph{Inequalities in household wealth across OECD countries: Evidence from the OECD.}
Organisation for Economic Co-operation and Development (OECD). 2018. [23-01-2019].\\
\url{http://www.oecd.org/officialdocuments/publicdisplaydocumentpdf/?cote=SDD/DOC(2018)1&docLanguage=En}

\bibitem{economy99percent}
Oxfam.\emph{An Econonomy for the 99\%.} 2017. [19-04-2018].\\
\url{https://www.oxfam.org/sites/www.oxfam.org/files/file_attachments/bp-economy-for-99-percent-160117-en.pdf}

\bibitem{IMF_moneytransformed}
Andersen, C.L. 2018. \textit{Money, transformed. The future of currency in a digital world.}
International Monetary Fund: Finance and Development. [10-06-2018]: Washington.\\
\url{https://www.imf.org/external/pubs/ft/fandd/2018/06/pdf/fd0618.pdf}

\bibitem{TokenInsight2018}
TokenInsight. 2018. \textit{2018 Exchange Cryptocurrency Anual Report.} [02-01-2019].\\
\url{https://tokeninsight.com}

\bibitem{imf_moneytransferred}
IMF. \emph{F\&D: money transferred.}  [20-06-2018].\\ \url{https://www.imf.org/external/pubs/ft/fandd/2018/06/pdf/fd0618.pdf}

\bibitem{GlobalFindexdatabase}
The World Bank. \emph{Adults lack account.} The Global Findex Database 2017. [10-02-2018].\\
\url{https://globalfindex.worldbank.org/globalfindex/sites/globalfindex/files/overview/211259ov.pdf}

\bibitem{IBM_blockchainfoodsupplychain}
IBM Food Trust. \emph{A new era for the world's food supply.}  [06-02-2019].\\
\url{https://www.ibm.com/blockchain/solutions/food-trust}


 % VIDEOS %
 \section*{Videos}

\bibitem{blockchain_or_bitcoin} 
Antonopoulos, A. 2016. Blockchain or Bitcoin: Understanding the differences.
A. Antonopoulos; [02-02-2017].\\ 
\url{https://youtu.be/mRQs9Y6CUSU}
 
\bibitem{introduction_to_bitcoin}
Antonopoulos, A. 2016. Introduction to Bitcoin.
A. Antonopoulos; [05-05-2017].\\
\url{https://antonopoulos.com/videos/}

\bibitem{future_of_money}
Antonopoulos, A. 2019. The Future of Money: How Bitcoin \& Blockchain Become The World's Currency.
A. Antonopoulos; [01-07-2019].\\
\url{https://www.youtube.com/watch?v=_aILeOqZEwY} 

\bibitem{money_as_a_system_of_control} Antonopoulos, A. 2017. Money as a system of control. A. Antonopoulos; [10-12-2017].\\ \url{https://www.youtube.com/watch?v=FyK4P7ZdOK8}
 
\bibitem{goldsilver ep1}
Goldsilver. 2013. Episode 1: Currency vs. Money.
M. Maloney; [05-02-2017].\\
\url{https://goldsilver.com/hidden-secrets/episode-1/}
 
\bibitem{goldsilver ep2}
Goldsilver. 2013. Episode 2: The 7 Stages of Empire.
M. Maloney; [10-02-2017].\\ \url{https://goldsilver.com/hidden-secrets/episode-2/}

\bibitem{goldsilver ep3}
Goldsilver. 2013. Episode 3: From Dollar Crisis to Golden Opportunity.
M. Maloney; [10-02-2017].\\ \url{https://goldsilver.com/hidden-secrets/episode-3/}

\bibitem{goldsilver ep4}
Goldsilver. 2013. Episode 4: The Biggest Scam in the History Of Mankind (in 7 Easy Steps).
M. Maloney; [11-02-2017].\\ \url{https://goldsilver.com/hidden-secrets/episode-4/}

\bibitem{goldsilver ep5}
Goldsilver. 2013. Episode 5: Rise of Hitler Was Economics.
M. Maloney; [11-02-2017].\\ \url{https://goldsilver.com/hidden-secrets/episode-5/}

\bibitem{goldsilver ep6}
Goldsilver. 2015. Episode 6: The Rollercoaster Crash.
M. Maloney; [12-02-2017].\\ \url{https://goldsilver.com/hidden-secrets/episode-6/}

\bibitem{goldsilver ep7}
Goldsilver. 2016. Episode 7: The USA's Day of Reckoning. M. Maloney; [12-02-2017].\\
\url{https://goldsilver.com/hidden-secrets/episode-7/}

\bibitem{goldsilver ep8}
Goldsilver. 2017. Episode 8: The Crypto Revolution.
M. Maloney; [18-12-2017].\\ \url{https://goldsilver.com/hidden-secrets/episode-8/}

\bibitem{goldsilver ep9}
Goldsilver. 2018. Episode 9: Fall of Empires: Rome vs USA.
M. Maloney; [01-11-2018].\\ \url{https://goldsilver.com/hidden-secrets/episode-9/}

\bibitem{goldsilver ep10}
Goldsilver. 2018. Episode 10: American Bread \& Circus. 
M. Maloney; [02-11-2018].\\ \url{https://goldsilver.com/hidden-secrets/episode-10/}

%%
% COURSES %
%%
\section*{Courses, Databases \& Others}

\bibitem{course:blockchain_usecases}
edX. 2018. Blockchain for Business. \emph{Blockchain technologies are changing industries}.
The Linux Foundation: LFS170x \& LFS171x.\\ \url{https://www.edx.org/professional-certificate/linuxfoundationx-blockchain-for-business}

\bibitem{course:fintech_introduction}
edX. 2019. FinTech. \emph{Cryptocurrencies, Blockchain \& AI are transforming finance}. 
Hong Kong University: HKU08x, HKU09x \& HKU10x.\\ \url{https://www.edx.org/professional-certificate/hkux-fintech}

\bibitem{tradingeconomics}
Trading Economics. \emph{International economic data.} [05-02-2019].\\
\url{https://tradingeconomics.com/}


\bibitem{coinmarketcap}
Coinmarketcap. \emph{Cryptocurrency market data.} [05-07-2019].\\
\url{https://coinmarketcap.com}

\bibitem{coingecko}
Coingecko. \emph{Overview of top 10 exchanges.} [05-02-2019].\\
\url{https://www.coingecko.com/en/exchanges}

\bibitem{blockonomi}
Blockonomi. \emph{Education: Wallets \& Exchanges Reviews} [01-05-2019].\\
\url{https://blockonomi.com}

\bibitem{hashemall}
Hashemall. \emph{Generic representation of cryptographic hash function(s).} [10-02-2018].\\
\url{http://www.hashemall.com}


 
 
\end{thebibliography}

\bibliography{tesis}